%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrywithsummary
    {} % Job title
    {Break, Startup} % Organization
    {Bangalore \& Kanpur, India} % Location
    {Sep. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setting up automated dev environment setup with vagrant and ansible.}
        \item {Created a GraphQL backend API in clojure with opensource implemetation of graphql library 'lacinia' by walmart.}
        \item {Developed the authenticatin and authorization scheme of users using encrypted Java web token to be used by various clients like web, mobile platforms.}
        \item {Worked on creating a web based admin panel in clojurescript using the Re-frame framework.}
        \item {Deployment of the application on AWS, setting up the servers, DNS and load balancer.}
        \item {Little work on react native mobile application for android using Facebook's open source client side implementation of GraphQL spec library called Relay.}
      \end{cvitems}
    }
    {
      \begin{cvsummary}
        I have been working on my own startup during this timeframe. Learned the paradigms of functional programming through clojure. Familiarize myself in the newest trend and hot technolgies in market e.g. React, GraphQL and AWS.
      \end{cvsummary}
    }

%---------------------------------------------------------
  \cventrywithsummary
    {Member Technical Staff, Sr. Software Engineer} % Job title
    {Amadeus Software Labs India Pvt Ltd} % Organization
    {Bangalore, India} % Location
    {Dec. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a scrum master in the team of 12 people. Co ordinating and planning various aspects of TPF decommissioning projects with stakeholders.}
        \item {Development of various libraries for shopping and reservation commands in a command line interface in C++}
        \item {Planning and executing gradual migration of newly written softwre in test and production.}
        \item {Writing test and doing regression testing, continuous integratio, production support.}
        \item {Developed the statistics collection framework for tracking traffic migration status of newly developed software. Collected statistics were loaded in a elastic search cluster for performing various queries on it.}
        \item {Worked on 'Kibana' for creating various views to offer real time migration status.}
        \item {Worked with DevOps and production support team to smoothly schedule and plan out the various migration activities.}
      \end{cvitems}
    }
    {
      \begin{cvsummary}
        I had been working in the hotel department handling the migration project. Old software written in TPF systems was being ported to the new stack(C++, unix). My work involved designing and development of the various backends used to handle the shopping and reservation of hotel bookings in GDS.
      \end{cvsummary}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Apr. 2013 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on enhancements of the reservation apis for hotel booking. Development done in C++.}
        \item {Worked on protocol buffer store database library to persist and retrieve new data.}
        \item {Migrating the source code from mercurial to git and implementing the git workflow for our team. }
        \item {Worked alongwith DevOps team to smooth out the development environment setup and continous delivery framework.}
        \item {Worked on compiler and various libraries migration to newer version, modifying the source code to take advantage of new language features.}
      \end{cvitems}
    }
%     {
%       \begin{cvsummary}
%         I have been instrumental in working on core part of hotel reservation and shopping apis.
%       \end{cvsummary}
%     }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team of 2 for development of a c++ backend responsible for managing the context switching between new and old software.}
        \item {Worked with memcached based context store for handling context.}
        \item {Created functionality to slowly migrate traffic and fallback to old software for various backends in hotel shopping apis.}
        \item {Writing test and doing regression testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrywithsummary
    {Software Engineer} % Job title
    {Ness Technologies (India) Pvt Ltd} % Organization
    {Bangalore, India} % Location
    {Sep. 2010 - Jun. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhancment of various shopping backends and worked on a C++ library to create the PNR display for hotel booking in a command line based tool.}
        \item {Unit testing the software with cppUnit.}
        \item {Worked on a database handling backend to migrate the interface from EDIFACT to XML.}
      \end{cvitems}
    }
    {
      \begin{cvsummary}
        I had been working in Ness Technologies for Amadeus in the hotel department.
      \end{cvsummary}
    }

%---------------------------------------------------------
  \cventrywithsummary
    {Freelancer} % Job title
    {Freelancing} % Organization
    {Kanpur, India} % Location
    {2009 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with various US clients to create fully XHTML and CSS compatible website template.}
        \item {Offered support for deploying their websites(nameserver config, email server config etc.)}
        \item {Worked on building dynamic websites based on Kohana PHP framework and managing them.}
      \end{cvitems}
    }
    {
      \begin{cvsummary}
        During graduation, started working part time for US clients building websites template, small content management systems.
      \end{cvsummary}
    }
%---------------------------------------------------------
\end{cventries}
